---
title: "Group Project Team 4"
author: "Catherine Vanaise"
date: "22/03/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#Loading the data
library(gsheet)
mydata <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1zcYomqhibeLyxaeTyJz8etOqUWqDLH_4/edit#gid=550557869")
```

```{r}
mydata$primEducGdp <- mydata$primEduc/mydata$gdp*100
mydata$lowSecEducGdp <- mydata$lowSecEduc/mydata$gdp*100
mydata$upSecEducGdp <- mydata$upSecEduc/mydata$gdp*100
mydata$longCycleTerEducGdp <- mydata$longCycleTerEduc/mydata$gdp*100
```

```{r}
if (!require("plm")) install.packages("plm")
library(plm)
```

Considering the results of the Hausman test that show a p-value of 0.03958, which is below 0.05, we need a fixed-effects model.

Model with control variables only

```{r}
modelControlF <- plm(unemployment ~  avRatio + adultEducTer,
             data = mydata, index = c("country", "year"), model = "within")
modelControlR <- plm(unemployment ~ avRatio + adultEducTer,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelControlF, modelControlR)

#need fixed
summary(modelControlF)
```

Model with primary education expenditure

```{r}
modelPrimEducF <- plm(unemployment ~  avRatio + adultEducTer + primEducGdp,
             data = mydata, index = c("country", "year"), model = "within")
modelPrimEducR <- plm(unemployment ~  avRatio + adultEducTer + primEducGdp,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelPrimEducF, modelPrimEducR)

#need fixed
summary(modelPrimEducF)
```

Model with lower secondary education expenditure

```{r}
modelLowSecEducF <- plm(unemployment ~  avRatio + adultEducTer + lowSecEducGdp,
             data = mydata, index = c("country", "year"), model = "within")
modelLowSecEducR <- plm(unemployment ~  avRatio + adultEducTer + lowSecEducGdp,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelLowSecEducF, modelLowSecEducR)

#need fixed
summary(modelLowSecEducF)
```

Model with upper secondary education expenditure

```{r}
modelUpSecEducF <- plm(unemployment ~  avRatio + adultEducTer + upSecEducGdp,
             data = mydata, index = c("country", "year"), model = "within")
modelUpSecEducR <- plm(unemployment ~  avRatio + adultEducTer + upSecEducGdp,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelUpSecEducF, modelUpSecEducR)

#need fixed
summary(modelUpSecEducF)
```

Model with long cycle tertiary education expenditure

```{r}
modelLongCycleEducF <- plm(unemployment ~  avRatio + adultEducTer + longCycleTerEducGdp,
             data = mydata, index = c("country", "year"), model = "within")
modelLongCycleEducR <- plm(unemployment ~  avRatio + adultEducTer + longCycleTerEducGdp,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelLongCycleEducF, modelLongCycleEducR)

#need fixed
summary(modelLongCycleEducF)
```


Region

```{r}
library(tidyverse)
mydata <- mydata %>% mutate(northAmerica = case_when(region == "North America" ~ 1
                                                      , TRUE ~ 0))
mydata <- mydata %>% mutate(southAmerica = case_when(region == "South America" ~ 1
                                                      , TRUE ~ 0))
mydata <- mydata %>% mutate(westernEurope = case_when(region == "Western" ~ 1
                                                      , TRUE ~ 0))
mydata <- mydata %>% mutate(easternEurope = case_when(region == "Eastern" ~ 1
                                                      , TRUE ~ 0))
mydata <- mydata %>% mutate(northernEurope = case_when(region == "Northern" ~ 1
                                                      , TRUE ~ 0))
mydata <- mydata %>% mutate(oceania = case_when(region == "Oceania" ~ 1
                                                      , TRUE ~ 0))
#middle east is with none of these (0 for all)
```

Primary Education

Model with primary education expenditure in North America

```{r}
modelPrimEducIntNAF <- plm(unemployment ~  avRatio + adultEducTer + primEducGdp*northAmerica,
             data = mydata, index = c("country", "year"), model = "within")
modelPrimEducIntNAR <- plm(unemployment ~  avRatio + adultEducTer + primEducGdp*northAmerica,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelPrimEducIntNAF, modelPrimEducIntNAR)

#need fixed
summary(modelPrimEducIntNAF)
```

Model with primary education expenditure in South America

```{r}
modelPrimEducIntSAF <- plm(unemployment ~  avRatio + adultEducTer + primEducGdp*southAmerica,
             data = mydata, index = c("country", "year"), model = "within")
modelPrimEducIntSAR <- plm(unemployment ~  avRatio + adultEducTer + primEducGdp*southAmerica,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelPrimEducIntSAF, modelPrimEducIntSAR)

#need fixed
summary(modelPrimEducIntSAF)
```

Model with primary education expenditure in Western Europe

```{r}
modelPrimEducIntWEF <- plm(unemployment ~  avRatio + adultEducTer + primEducGdp*westernEurope,
             data = mydata, index = c("country", "year"), model = "within")
modelPrimEducIntWER <- plm(unemployment ~  avRatio + adultEducTer + primEducGdp*westernEurope,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelPrimEducIntWEF, modelPrimEducIntWER)

#need fixed
summary(modelPrimEducIntWEF)
```

Model with primary education expenditure in Eastern Europe

```{r}
modelPrimEducIntEEF <- plm(unemployment ~  avRatio + adultEducTer + primEducGdp*easternEurope,
             data = mydata, index = c("country", "year"), model = "within")
modelPrimEducIntEER <- plm(unemployment ~  avRatio + adultEducTer + primEducGdp*easternEurope,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelPrimEducIntEEF, modelPrimEducIntEER)

#need fixed
summary(modelPrimEducIntEEF)
```

Model with primary education expenditure in Northern Europe

```{r}
modelPrimEducIntNEF <- plm(unemployment ~  avRatio + adultEducTer + primEducGdp*northernEurope,
             data = mydata, index = c("country", "year"), model = "within")
modelPrimEducIntNER <- plm(unemployment ~  avRatio + adultEducTer + primEducGdp*northernEurope,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelPrimEducIntNEF, modelPrimEducIntNER)

#need fixed
summary(modelPrimEducIntNEF)
```

Model with primary education expenditure in Oceania

```{r}
modelPrimEducIntOF <- plm(unemployment ~  avRatio + adultEducTer + primEducGdp*oceania,
             data = mydata, index = c("country", "year"), model = "within")
modelPrimEducIntOR <- plm(unemployment ~  avRatio + adultEducTer + primEducGdp*oceania,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelPrimEducIntNEF, modelPrimEducIntNER)

#need fixed
summary(modelPrimEducIntOF)
```

Lower Secondary Education

Model with lower secondary education expenditure in North America

```{r}
modelLowSecEducIntNAF <- plm(unemployment ~  avRatio + adultEducTer + lowSecEducGdp*northAmerica,
             data = mydata, index = c("country", "year"), model = "within")
modelLowSecEducIntNAR <- plm(unemployment ~  avRatio + adultEducTer + lowSecEducGdp*northAmerica,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelLowSecEducIntNAF, modelLowSecEducIntNAR)

#need fixed
summary(modelLowSecEducIntNAF)
```

Model with lower secondary education expenditure in South America

```{r}
modelLowSecEducIntSAF <- plm(unemployment ~  avRatio + adultEducTer + lowSecEducGdp*southAmerica,
             data = mydata, index = c("country", "year"), model = "within")
modelLowSecEducIntSAR <- plm(unemployment ~  avRatio + adultEducTer + lowSecEducGdp*southAmerica,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelLowSecEducIntSAF, modelLowSecEducIntSAR)

#need fixed
summary(modelPrimEducIntSAF)
```

Model with lower secondary education expenditure in Western Europe

```{r}
modelLowSecEducIntWEF <- plm(unemployment ~  avRatio + adultEducTer + lowSecEducGdp*westernEurope,
             data = mydata, index = c("country", "year"), model = "within")
modelLowSecEducIntWER <- plm(unemployment ~  avRatio + adultEducTer + lowSecEducGdp*westernEurope,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelLowSecEducIntWEF, modelLowSecEducIntWER)

#need fixed
summary(modelLowSecEducIntWEF)
```

Model with lower secondary education expenditure in Eastern Europe

```{r}
modelLowSecEducIntEEF <- plm(unemployment ~  avRatio + adultEducTer + lowSecEducGdp*easternEurope,
             data = mydata, index = c("country", "year"), model = "within")
modelLowSecEducIntEER <- plm(unemployment ~  avRatio + adultEducTer + lowSecEducGdp*easternEurope,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelLowSecEducIntEEF, modelLowSecEducIntEER)

#need fixed
summary(modelLowSecEducIntEEF)
```

Model with lower secondary education expenditure in Northern Europe

```{r}
modelLowSecEducIntNEF <- plm(unemployment ~  avRatio + adultEducTer + lowSecEducGdp*northernEurope,
             data = mydata, index = c("country", "year"), model = "within")
modelLowSecEducIntNER <- plm(unemployment ~  avRatio + adultEducTer + lowSecEducGdp*northernEurope,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelLowSecEducIntNEF, modelLowSecEducIntNER)

#need fixed
summary(modelLowSecEducIntNEF)
```

Model with lower secondary education expenditure in Oceania

```{r}
modelLowSecEducIntOF <- plm(unemployment ~  avRatio + adultEducTer + lowSecEducGdp*oceania,
             data = mydata, index = c("country", "year"), model = "within")
modelLowSecEducIntOR <- plm(unemployment ~  avRatio + adultEducTer + lowSecEducGdp*oceania,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelLowSecEducIntNEF, modelLowSecEducIntNER)

#need fixed
summary(modelLowSecEducIntOF)
```


Upper Secondary Education

Model with upper secondary education expenditure in North America

```{r}
modelUpSecEducIntNAF <- plm(unemployment ~  avRatio + adultEducTer + upSecEducGdp*northAmerica,
             data = mydata, index = c("country", "year"), model = "within")
modelUpSecEducIntNAR <- plm(unemployment ~  avRatio + adultEducTer + upSecEducGdp*northAmerica,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelUpSecEducIntNAF, modelUpSecEducIntNAR)

#need fixed
summary(modelUpSecEducIntNAF)
```

Model with upper secondary education expenditure in South America

```{r}
modelUpSecEducIntSAF <- plm(unemployment ~  avRatio + adultEducTer + upSecEducGdp*southAmerica,
             data = mydata, index = c("country", "year"), model = "within")
modelUpSecEducIntSAR <- plm(unemployment ~  avRatio + adultEducTer + upSecEducGdp*southAmerica,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelUpSecEducIntNAF, modelUpSecEducIntNAR)

#need fixed
summary(modelUpSecEducIntSAF)
```

Model with upper secondary education expenditure in Western Europe

```{r}
modelUpSecEducIntWEF <- plm(unemployment ~  avRatio + adultEducTer + upSecEducGdp*westernEurope,
             data = mydata, index = c("country", "year"), model = "within")
modelUpSecEducIntWER <- plm(unemployment ~  avRatio + adultEducTer + upSecEducGdp*westernEurope,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelUpSecEducIntWEF, modelUpSecEducIntWER)

#need fixed
summary(modelUpSecEducIntWEF)
```

Model with upper secondary education expenditure in Eastern Europe

```{r}
modelUpSecEducIntEEF <- plm(unemployment ~  avRatio + adultEducTer + upSecEducGdp*easternEurope,
             data = mydata, index = c("country", "year"), model = "within")
modelUpSecEducIntEER <- plm(unemployment ~  avRatio + adultEducTer + upSecEducGdp*easternEurope,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelUpSecEducIntEEF, modelUpSecEducIntEER)

#need fixed
summary(modelUpSecEducIntEEF)
```

Model with upper secondary education expenditure in Northern Europe

```{r}
modelUpSecEducIntNEF <- plm(unemployment ~  avRatio + adultEducTer + upSecEducGdp*northernEurope,
             data = mydata, index = c("country", "year"), model = "within")
modelUpSecEducIntNER <- plm(unemployment ~  avRatio + adultEducTer + upSecEducGdp*northernEurope,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelUpSecEducIntNEF, modelUpSecEducIntNER)

#need fixed
summary(modelUpSecEducIntNEF)
```

Model with upper secondary education expenditure in Oceania

```{r}
modelUpSecEducIntOF <- plm(unemployment ~  avRatio + adultEducTer + upSecEducGdp*oceania,
             data = mydata, index = c("country", "year"), model = "within")
modelUpSecEducIntOR <- plm(unemployment ~  avRatio + adultEducTer + upSecEducGdp*oceania,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelUpSecEducIntNEF, modelUpSecEducIntNER)

#need fixed
summary(modelUpSecEducIntOF)
```


Long Cycle Tertiary Education

Model with long cycle tertiary education expenditure in North America

```{r}
modelLongCycleTerEducIntNAF <- plm(unemployment ~  avRatio + adultEducTer + longCycleTerEducGdp*northAmerica,
             data = mydata, index = c("country", "year"), model = "within")
modelLongCycleTerEducIntNAR <- plm(unemployment ~  avRatio + adultEducTer + longCycleTerEducGdp*northAmerica,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelLongCycleTerEducIntNAF, modelLongCycleTerEducIntNAR)

#need fixed
summary(modelLongCycleTerEducIntNAF)
```

Model with long cycle tertiary education expenditure in South America

```{r}
modelLongCycleTerEducIntSAF <- plm(unemployment ~  avRatio + adultEducTer + longCycleTerEducGdp*southAmerica,
             data = mydata, index = c("country", "year"), model = "within")
modelLongCycleTerEducIntSAR <- plm(unemployment ~  avRatio + adultEducTer + longCycleTerEducGdp*southAmerica,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelLongCycleTerEducIntNAF, modelLongCycleTerEducIntNAR)

#need fixed
summary(modelLongCycleTerEducIntSAF)
```

Model with long cycle tertiary education expenditure in Western Europe

```{r}
modelLongCycleTerEducIntWEF <- plm(unemployment ~  avRatio + adultEducTer + longCycleTerEducGdp*westernEurope,
             data = mydata, index = c("country", "year"), model = "within")
modelLongCycleTerEducIntWER <- plm(unemployment ~  avRatio + adultEducTer + longCycleTerEducGdp*westernEurope,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelLongCycleTerEducIntWEF, modelLongCycleTerEducIntWER)

#need fixed
summary(modelLongCycleTerEducIntWEF)
```

Model with long cycle tertiary education expenditure in Eastern Europe

```{r}
modelLongCycleTerEducIntEEF <- plm(unemployment ~  avRatio + adultEducTer + longCycleTerEducGdp*easternEurope,
             data = mydata, index = c("country", "year"), model = "within")
modelLongCycleTerEducIntEER <- plm(unemployment ~  avRatio + adultEducTer + longCycleTerEducGdp*easternEurope,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelLongCycleTerEducIntEEF, modelLongCycleTerEducIntEER)

#need fixed
summary(modelLongCycleTerEducIntEEF)
```

Model with long cycle tertiary education expenditure in Northern Europe

```{r}
modelLongCycleTerEducIntNEF <- plm(unemployment ~  avRatio + adultEducTer + longCycleTerEducGdp*northernEurope,
             data = mydata, index = c("country", "year"), model = "within")
modelLongCycleTerEducIntNER <- plm(unemployment ~  avRatio + adultEducTer + longCycleTerEducGdp*northernEurope,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelLongCycleTerEducIntNEF, modelLongCycleTerEducIntNER)

#need fixed
summary(modelLongCycleTerEducIntNEF)
```

Model with long cycle tertiary education expenditure in Oceania

```{r}
modelLongCycleTerEducIntOF <- plm(unemployment ~  avRatio + adultEducTer + longCycleTerEducGdp*oceania,
             data = mydata, index = c("country", "year"), model = "within")
modelLongCycleTerEducIntOR <- plm(unemployment ~  avRatio + adultEducTer + longCycleTerEducGdp*oceania,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelLongCycleTerEducIntNEF, modelLongCycleTerEducIntNER)

#need fixed
summary(modelLongCycleTerEducIntOF)
```



Income

```{r}
quantile(mydata$gdpph, probs = c(0, 0.25, 0.5, 0.75, 1))
```


```{r}
library(tidyverse)
quantile(mydata$gdpph, probs = c(0, 0.25, 0.5, 0.75, 1))

mydata <- mydata %>% mutate(lowerMiddle = case_when(26725.26 < gdpph < 33643.00 ~ 1
                                                      , TRUE ~ 0))
mydata <- mydata %>% mutate(upperMiddle = case_when(33643.01 < gdpph <  43618.75~ 1
                                                      , TRUE ~ 0))
mydata <- mydata %>% mutate(upper = case_when(43618.75 < gdpph < 87496 ~ 1
                                                      , TRUE ~ 0))

#lower is with none of these (0 for all)
```

```{r}
mydata$lowerMiddle<-0
mydata$lowerMiddle[mydata$gdpph>=26725.25&mydata$gdpph<33643]<-1

mydata$upperMiddle<-0
mydata$upperMiddle[mydata$gdpph>=33643&mydata$gdpph<43618.75]<-1

mydata$upper<-0
mydata$upper[mydata$gdpph>=43618.75&mydata$gdpph<87496]<-1
```

Primary Education

Model with primary education expenditure in Lower Middle Income

```{r}
library(plm)
modelPrimEducIntLMF <- plm(unemployment ~  avRatio + adultEducTer + primEducGdp*lowerMiddle,
             data = mydata, index = c("country", "year"), model = "within")
modelPrimEducIntLMR <- plm(unemployment ~  avRatio + adultEducTer + primEducGdp*lowerMiddle,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelPrimEducIntLMF, modelPrimEducIntLMR)

#need fixed
summary(modelPrimEducIntLMF)
```

Model with primary education expenditure in Upper Middle Income

```{r}
library(plm)
modelPrimEducIntUMF <- plm(unemployment ~  avRatio + adultEducTer + primEducGdp*upperMiddle,
             data = mydata, index = c("country", "year"), model = "within")
modelPrimEducIntUMR <- plm(unemployment ~  avRatio + adultEducTer + primEducGdp*upperMiddle,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelPrimEducIntUMF, modelPrimEducIntUMR)

#need fixed
summary(modelPrimEducIntUMF)
```

Model with primary education expenditure in Upper Income

```{r}
library(plm)
modelPrimEducIntUF <- plm(unemployment ~  avRatio + adultEducTer + primEducGdp*upper,
             data = mydata, index = c("country", "year"), model = "within")
modelPrimEducIntUR <- plm(unemployment ~  avRatio + adultEducTer + primEducGdp*upper,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelPrimEducIntUF, modelPrimEducIntUR)

#need fixed
summary(modelPrimEducIntUF)
```


Lower Secondary Education

Model with lower secondary expenditure in Lower Middle Income

```{r}
library(plm)
modelLowSecEducIntLMF <- plm(unemployment ~  avRatio + adultEducTer + lowSecEducGdp*lowerMiddle,
             data = mydata, index = c("country", "year"), model = "within")
modelLowSecEducIntLMR <- plm(unemployment ~  avRatio + adultEducTer + lowSecEducGdp*lowerMiddle,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelLowSecEducIntLMF, modelLowSecEducIntLMR)

#need fixed
summary(modelLowSecEducIntLMF)
```

Model with lower secondary education expenditure in Upper Middle Income

```{r}
library(plm)
modelLowSecEducIntUMF <- plm(unemployment ~  avRatio + adultEducTer + lowSecEducGdp*upperMiddle,
             data = mydata, index = c("country", "year"), model = "within")
modelLowSecEducIntUMR <- plm(unemployment ~  avRatio + adultEducTer + lowSecEducGdp*upperMiddle,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelLowSecEducIntUMF, modelLowSecEducIntUMR)

#need fixed
summary(modelLowSecEducIntUMF)
```

Model with lower secondary education expenditure in Upper Income

```{r}
library(plm)
modelLowSecEducIntUF <- plm(unemployment ~  avRatio + adultEducTer + lowSecEducGdp*upper,
             data = mydata, index = c("country", "year"), model = "within")
modelLowSecEducIntUR <- plm(unemployment ~  avRatio + adultEducTer + lowSecEducGdp*upper,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelLowSecEducIntUF, modelUpSecEducIntUR)

#need fixed
summary(modelLowSecEducIntUF)
```


Upper Secondary Education

Model with upper secondary expenditure in Lower Middle Income

```{r}
library(plm)
modelUpSecEducIntLMF <- plm(unemployment ~  avRatio + adultEducTer + upSecEducGdp*lowerMiddle,
             data = mydata, index = c("country", "year"), model = "within")
modelUpSecEducIntLMR <- plm(unemployment ~  avRatio + adultEducTer + upSecEducGdp*lowerMiddle,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelUpSecEducIntLMF, modelUpSecEducIntLMR)

#need fixed
summary(modelUpSecEducIntLMF)
```

Model with upper secondary education expenditure in Upper Middle Income

```{r}
library(plm)
modelUpSecEducIntUMF <- plm(unemployment ~  avRatio + adultEducTer + upSecEducGdp*upperMiddle,
             data = mydata, index = c("country", "year"), model = "within")
modelUpSecEducIntUMR <- plm(unemployment ~  avRatio + adultEducTer + upSecEducGdp*upperMiddle,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelUpSecEducIntUMF, modelUpSecEducIntUMR)

#need fixed
summary(modelUpSecEducIntUMF)
```

Model with upper secondary education expenditure in Upper Income

```{r}
library(plm)
modelUpSecEducIntUF <- plm(unemployment ~  avRatio + adultEducTer + upSecEducGdp*upper,
             data = mydata, index = c("country", "year"), model = "within")
modelUpSecEducIntUR <- plm(unemployment ~  avRatio + adultEducTer + upSecEducGdp*upper,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelUpSecEducIntUF, modelUpSecEducIntUR)

#need fixed
summary(modelUpSecEducIntUF)
```


Long Cycle Tertiary Education

Model with long cycle tertiary expenditure in Lower Middle Income

```{r}
library(plm)
modelLongCycleTerEducIntLMF <- plm(unemployment ~  avRatio + adultEducTer + longCycleTerEducGdp*lowerMiddle,
             data = mydata, index = c("country", "year"), model = "within")
modelLongCycleTerEducIntLMR <- plm(unemployment ~  avRatio + adultEducTer + longCycleTerEducGdp*lowerMiddle,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelLongCycleTerEducIntLMF, modelLongCycleTerEducIntLMR)

#need fixed
summary(modelLongCycleTerEducIntLMF)
```

Model with long cycle tertiary education expenditure in Upper Middle Income

```{r}
library(plm)
modelLongCycleTerEducIntUMF <- plm(unemployment ~  avRatio + adultEducTer + longCycleTerEducGdp*upperMiddle,
             data = mydata, index = c("country", "year"), model = "within")
modelLongCycleTerEducIntUMR <- plm(unemployment ~  avRatio + adultEducTer + longCycleTerEducGdp*upperMiddle,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelLongCycleTerEducIntUMF, modelLongCycleTerEducIntUMR)

#need fixed
summary(modelLongCycleTerEducIntUMF)
```

Model with long cycle tertiary education expenditure in Upper Income

```{r}
library(plm)
modelLongCycleTerEducIntUF <- plm(unemployment ~  avRatio + adultEducTer + longCycleTerEducGdp*upper,
             data = mydata, index = c("country", "year"), model = "within")
modelLongCycleTerEducIntUR <- plm(unemployment ~  avRatio + adultEducTer + longCycleTerEducGdp*upper,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelLongCycleTerEducIntUF, modelLongCycleTerEducIntUR)

#need fixed
summary(modelLongCycleTerEducIntUF)
```

```{r}

```

```{r}

```

