---
title: "Group Project Team 4"
author: "Catherine Vanaise"
date: "22/03/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#Loading the data
library(gsheet)
mydata <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1zcYomqhibeLyxaeTyJz8etOqUWqDLH_4/edit#gid=550557869")
```

```{r}
mydata$primEducGdp <- mydata$primEduc/mydata$gdp*100
mydata$lowSecEducGdp <- mydata$lowSecEduc/mydata$gdp*100
mydata$upSecEducGdp <- mydata$upSecEduc/mydata$gdp*100
mydata$longCycleTerEducGdp <- mydata$longCycleTerEduc/mydata$gdp*100
```

```{r}
if (!require("plm")) install.packages("plm")
library(plm)
```

We must first determine if we need a fixed-effects model to help remove the effects of time-invariant characteristics (such as the countries and years). If fixed-effects do affect the model, it is important to control for them to ensure that the model will then be truly measuring the impact of the independent variables on the dependent variable. 

Considering the results of the Hausman test for all models that show a p-value lower than 0.05, we need a fixed-effects model.

Model with control variables only

```{r}
modelControlF <- plm(unemployment ~  avRatio + adultEducTer,
             data = mydata, index = c("country", "year"), model = "within")
modelControlR <- plm(unemployment ~ avRatio + adultEducTer,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelControlF, modelControlR)

#need fixed
summary(modelControlF)
```

Model with primary education expenditure

```{r}
modelPrimEducF <- plm(unemployment ~  avRatio + adultEducTer + primEducGdp,
             data = mydata, index = c("country", "year"), model = "within")
modelPrimEducR <- plm(unemployment ~  avRatio + adultEducTer + primEducGdp,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelPrimEducF, modelPrimEducR)

#need fixed
summary(modelPrimEducF)
```

Model with lower secondary education expenditure

```{r}
modelLowSecEducF <- plm(unemployment ~  avRatio + adultEducTer + lowSecEducGdp,
             data = mydata, index = c("country", "year"), model = "within")
modelLowSecEducR <- plm(unemployment ~  avRatio + adultEducTer + lowSecEducGdp,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelLowSecEducF, modelLowSecEducR)

#need fixed
summary(modelLowSecEducF)
```

Model with upper secondary education expenditure

```{r}
modelUpSecEducF <- plm(unemployment ~  avRatio + adultEducTer + upSecEducGdp,
             data = mydata, index = c("country", "year"), model = "within")
modelUpSecEducR <- plm(unemployment ~  avRatio + adultEducTer + upSecEducGdp,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelUpSecEducF, modelUpSecEducR)

#need fixed
summary(modelUpSecEducF)
```

# Model with long cycle tertiary education expenditure

```{r}
modelLongCycleEducF <- plm(unemployment ~  avRatio + adultEducTer + longCycleTerEducGdp,
             data = mydata, index = c("country", "year"), model = "within")
modelLongCycleEducR <- plm(unemployment ~  avRatio + adultEducTer + longCycleTerEducGdp,
             data = mydata, index = c("country", "year"), model = "random")
phtest(modelLongCycleEducF, modelLongCycleEducR)

#need fixed
summary(modelLongCycleEducF)
```


Region

```{r}
library(tidyverse)
mydata <- mydata %>% mutate(northAmerica = case_when(region == "North America" ~ 1
                                                      , TRUE ~ 0))
mydata <- mydata %>% mutate(southAmerica = case_when(region == "South America" ~ 1
                                                      , TRUE ~ 0))
mydata <- mydata %>% mutate(westernEurope = case_when(region == "Western" ~ 1
                                                      , TRUE ~ 0))
mydata <- mydata %>% mutate(easternEurope = case_when(region == "Eastern" ~ 1
                                                      , TRUE ~ 0))
mydata <- mydata %>% mutate(northernEurope = case_when(region == "Northern" ~ 1
                                                      , TRUE ~ 0))
mydata <- mydata %>% mutate(oceania = case_when(region == "Oceania" ~ 1
                                                      , TRUE ~ 0))
#middle east is with none of these (0 for all)
```

Model with primary education with region dummy

```{r}
modelPrimEducIntALLF <- plm(unemployment ~  avRatio + adultEducTer + primEducGdp*northAmerica +primEducGdp*southAmerica + primEducGdp*westernEurope + primEducGdp*easternEurope + primEducGdp*northernEurope + primEducGdp*oceania,
             data = mydata, index = c("country", "year"), model = "within")

summary(modelPrimEducIntALLF)

```

Model with lower secondary education with region dummy

```{r}
modelLowSecEducIntALLF <- plm(unemployment ~  avRatio + adultEducTer + lowSecEducGdp*northAmerica + lowSecEducGdp*southAmerica + lowSecEducGdp*westernEurope + lowSecEducGdp*easternEurope + lowSecEducGdp*northernEurope + lowSecEducGdp*oceania,
             data = mydata, index = c("country", "year"), model = "within")

summary(modelLowSecEducIntALLF)

```

Model with upper secondary education with region dummy

```{r}
modelUpSecEducIntALLF <- plm(unemployment ~  avRatio + adultEducTer + upSecEducGdp*northAmerica + upSecEducGdp*southAmerica + upSecEducGdp*westernEurope + upSecEducGdp*easternEurope + upSecEducGdp*northernEurope + upSecEducGdp*oceania,
             data = mydata, index = c("country", "year"), model = "within")

summary(modelUpSecEducIntALLF)

```

Model with long cycle tertiary education with region dummy

```{r}
modelLongCycleTerEducIntALLF <- plm(unemployment ~  avRatio + adultEducTer + longCycleTerEducGdp*northAmerica + longCycleTerEducGdp*southAmerica + longCycleTerEducGdp*westernEurope + longCycleTerEducGdp*easternEurope + longCycleTerEducGdp*northernEurope + longCycleTerEducGdp*oceania,
             data = mydata, index = c("country", "year"), model = "within")

summary(modelLongCycleTerEducIntALLF)

```




Income

```{r}
quantile(mydata$gdpph, probs = c(0, 0.25, 0.5, 0.75, 1))
```


```{r}
mydata$lowerMiddle<-0
mydata$lowerMiddle[mydata$gdpph>=26725.25&mydata$gdpph<33643]<-1

mydata$upperMiddle<-0
mydata$upperMiddle[mydata$gdpph>=33643&mydata$gdpph<43618.75]<-1

mydata$upper<-0
mydata$upper[mydata$gdpph>=43618.75&mydata$gdpph<=87496]<-1
```


Model with primary education with region income

```{r}
modelPrimEducIntIncomeALLF <- plm(unemployment ~  avRatio + adultEducTer + primEducGdp*lowerMiddle +primEducGdp*upperMiddle + primEducGdp*upper,
             data = mydata, index = c("country", "year"), model = "within")

summary(modelPrimEducIntIncomeALLF)

```

Model with lower secondary education with region dummy

```{r}
modelLowSecEducIntIncomeALLF <- plm(unemployment ~  avRatio + adultEducTer + lowSecEducGdp*lowerMiddle + lowSecEducGdp*upperMiddle + lowSecEducGdp*upper,
             data = mydata, index = c("country", "year"), model = "within")

summary(modelLowSecEducIntIncomeALLF)

```

Model with upper secondary education with region dummy

```{r}
modelUpSecEducIntIncomeALLF <- plm(unemployment ~  avRatio + adultEducTer + upSecEducGdp*lowerMiddle + upSecEducGdp*upperMiddle + upSecEducGdp*upper,
             data = mydata, index = c("country", "year"), model = "within")

summary(modelUpSecEducIntIncomeALLF)

```

Model with long cycle tertiary education with region dummy

```{r}
modelLongCycleTerEducIntIncomeALLF <- plm(unemployment ~  avRatio + adultEducTer + longCycleTerEducGdp*lowerMiddle + longCycleTerEducGdp*upperMiddle + longCycleTerEducGdp*upper,
             data = mydata, index = c("country", "year"), model = "within")

summary(modelLongCycleTerEducIntIncomeALLF)

```






```{r}

```

```{r}

```

